The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-10 paper/ms.tex
wording

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third brightest and sixth-brightest stars on silicon, making these the brightest stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

>>>>

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. A detailed study of these stars will be presented by Antoci et al., in prep.
